PREPRINT -- Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery -- PREPRINT.

### 2024-03-09 docs/_tex/index.tex
laurent's comments

The primary objective of this study was to develop a method for the
accurate classification of macrophytes on intertidal mudflats,
specifically focusing on distinguishing between Chlorophyceae (green
macroalgae) and marine Magnoliopsida (seagrasses) using multispectral
drone data. The ability to differentiate between various types of
vegetation, as demonstrated in this study, plays a critical role in
ecological monitoring and management. By distinguishing between
seagrasses and macroalgae, our approach facilitates targeted
conservation strategies, enabling more effective preservation and
restoration efforts in coastal ecosystems. The discrimination of
seagrasses from green macroalgae presents significant challenges
\citetext{\citealp[ ]{oiry2021using}; \citealp{Bannari2022}}, primarily
due to the shared pigment composition between these taxa
\citep{mckenzie2020global}, as depicted in Figure~\ref{fig-Pigm} but
also by the frequent spatial mixing of these green macrophytes. These
green macrophytes have in common photosynthtic pigmetns, chlorophyll a
and b, and accessory carotenoid pigments zeaxantin, lutein and
neoxanthin. As a result the spectral signatures are often
indistinguishable in the visible wavelength region. This spectral
overlap is further complicated by the intermingling of seagrasses and
green macroalgae in the same spatial locations, posing a significant
challenge for remote sensing aimed at accurately mapping and monitoring
coastal ecosystems. Our study addresses these complexities by using
high-resolution drone imagery with 10 spectral bands. \citep{Davies2023}
have shown that having at least eight spectral bands ranging between 500
nm to 850 nm including a green band at 530 nm and another one in the
RedEdge region at 730 nm was crucial to accurately discriminate green
macrophytes.

@@

The utilization of very high-resolution drone-based remote sensing
coupled with machine learning techniques has proven to be an effective
method for the discrimination of seagrasses from green macroalgae with a
multispectral resolution sensor. Standardized reflectance were
incorporated in the Neural Network model allowing for a better
discrimination of spectral features related to pigment absorption in the
visible. There was a striking difference for the variable of importance
to discriminate Magnoliopsida from Chlorophyceae. The latter was
essentially identify with the 451 nm spectral band while more spetral
bands were needed to identify the former, notably 650, 560, 668, and 705
nm. As the spectral bands of the Micasense RedEdge Dual MX are very
similar to those of Sentinel-2, we suggest that multispectral satellite
data have the potential to perform this discrimination between green
macrophytes. The algorithm should now be adapted to Sentinel-2 with all
the drone data from this study that can be used as training and
validation data. The findings underscore the importance of adopting
advanced remote sensing tools in ecological studies and environmental
monitoring, providing a foundation for future research and policy
implementation aimed at ecosystem preservation and restoration.

>>>>

The primary objective of this study was to develop a method for the
accurate classification of macrophytes on intertidal mudflats,
specifically focusing on distinguishing between Chlorophyceae (green
macroalgae) and marine Magnoliopsida (seagrasses) using multispectral
drone data. The ability to differentiate between various types of
vegetation, as demonstrated in this study, plays a critical role in
ecological monitoring and management. By distinguishing between
seagrasses and macroalgae, our approach facilitates targeted
conservation strategies, enabling more effective preservation and
restoration efforts in coastal ecosystems. The discrimination of
seagrasses from green macroalgae presents significant challenges
\citetext{\citealp[ ]{oiry2021using}; \citealp{bannari2022}}, primarily
due to the shared pigment composition between these taxa
\citep{mckenzie2020global}, as depicted in Figure~\ref{fig-Pigm} but
also by the frequent spatial mixing of these green macrophytes. These
green macrophytes have in common photosynthtic pigmetns, chlorophyll a
and b, and accessory carotenoid pigments zeaxantin, lutein and
neoxanthin. As a result the spectral signatures are often
indistinguishable in the visible wavelength region. This spectral
overlap is further complicated by the intermingling of seagrasses and
green macroalgae in the same spatial locations, posing a significant
challenge for remote sensing aimed at accurately mapping and monitoring
coastal ecosystems. Our study addresses these complexities by using
high-resolution drone imagery with 10 spectral bands. \citep{Davies2023}
have shown that having at least eight spectral bands ranging between 500
nm to 850 nm including a green band at 530 nm and another one in the
RedEdge region at 730 nm was crucial to accurately discriminate green
macrophytes.

@@

The utilization of very high-resolution drone-based remote sensing
coupled with machine learning techniques has proven to be an effective
method for the discrimination of seagrasses from green macroalgae with a
multispectral resolution sensor. Standardized reflectance were
incorporated in the Neural Network model allowing for a better
discrimination of spectral features related to pigment absorption in the
visible. There was a striking difference for the variable of importance
to discriminate Magnoliopsida from Chlorophyceae. The latter was
essentially identify with the 451 nm spectral band while more spectral
bands were needed to identify the former, notably 650, 560, 668, and 705
nm. As the spectral bands of the Micasense RedEdge Dual MX are very
similar to those of Sentinel-2, we suggest that multispectral satellite
data have the potential to perform this discrimination between green
macrophytes. The algorithm should now be adapted to Sentinel-2 with all
the drone data from this study that can be used as training and
validation data. The findings underscore the importance of adopting
advanced remote sensing tools in ecological studies and environmental
monitoring, providing a foundation for future research and policy
implementation aimed at ecosystem preservation and restoration.

### 2024-03-09 index.qmd
laurent's comments

The primary objective of this study was to develop a method for the accurate classification of macrophytes on intertidal mudflats, specifically focusing on distinguishing between Chlorophyceae (green macroalgae) and marine Magnoliopsida (seagrasses) using multispectral drone data. The ability to differentiate between various types of vegetation, as demonstrated in this study, plays a critical role in ecological monitoring and management. By distinguishing between seagrasses and macroalgae, our approach facilitates targeted conservation strategies, enabling more effective preservation and restoration efforts in coastal ecosystems. The discrimination of seagrasses from green macroalgae presents significant challenges [@oiry2021using ; @Bannari2022], primarily due to the shared pigment composition between these taxa [@mckenzie2020global], as depicted in @fig-Pigm but also by the frequent spatial mixing of these green macrophytes. These green macrophytes have in common photosynthtic pigmetns, chlorophyll a and b, and accessory carotenoid pigments zeaxantin, lutein and neoxanthin. As a result the spectral signatures are often indistinguishable in the visible wavelength region. This spectral overlap is further complicated by the intermingling of seagrasses and green macroalgae in the same spatial locations, posing a significant challenge for remote sensing aimed at accurately mapping and monitoring coastal ecosystems. Our study addresses these complexities by using high-resolution drone imagery with 10 spectral bands. @Davies2023 have shown that having at least eight spectral bands ranging between 500 nm to 850 nm including a green band at 530 nm and another one in the RedEdge region at 730 nm was crucial to accurately discriminate green macrophytes.

>>>>

The primary objective of this study was to develop a method for the accurate classification of macrophytes on intertidal mudflats, specifically focusing on distinguishing between Chlorophyceae (green macroalgae) and marine Magnoliopsida (seagrasses) using multispectral drone data. The ability to differentiate between various types of vegetation, as demonstrated in this study, plays a critical role in ecological monitoring and management. By distinguishing between seagrasses and macroalgae, our approach facilitates targeted conservation strategies, enabling more effective preservation and restoration efforts in coastal ecosystems. The discrimination of seagrasses from green macroalgae presents significant challenges [@oiry2021using ; @bannari2022], primarily due to the shared pigment composition between these taxa [@mckenzie2020global], as depicted in @fig-Pigm but also by the frequent spatial mixing of these green macrophytes. These green macrophytes have in common photosynthtic pigmetns, chlorophyll a and b, and accessory carotenoid pigments zeaxantin, lutein and neoxanthin. As a result the spectral signatures are often indistinguishable in the visible wavelength region. This spectral overlap is further complicated by the intermingling of seagrasses and green macroalgae in the same spatial locations, posing a significant challenge for remote sensing aimed at accurately mapping and monitoring coastal ecosystems. Our study addresses these complexities by using high-resolution drone imagery with 10 spectral bands. @Davies2023 have shown that having at least eight spectral bands ranging between 500 nm to 850 nm including a green band at 530 nm and another one in the RedEdge region at 730 nm was crucial to accurately discriminate green macrophytes.
